---
title: "ParSPaS: Simple Example"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{my-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(ParSPaS)
```

# ParSPaS: Partial Solution Path Stability

Partial Solution Path Stability (ParSPaS) is a model selection framework for Generalised Linear Models when the Lasso estimator is used.

## Installation

```r
library(devtools)
devtools::install_github("smithconnor/ParSPaS")
```

## An example

We simulate a dataset with 100 observations and 10 varaibles.

We apply the ParSPaS method to visualise varaible stability and present the resulting plots.

```{r, eval = TRUE}
library(ParSPaS)

## Data simulation
set.seed(1234)
n = 100
p = 10
varNames = paste0("X", 1:p)
beta = c(2,-1,-1, rep(x = 0, 
                      times = p - 3))
x = matrix(rnorm(n*p),
           ncol = p)
colnames(x) = varNames
y = rbinom(n = n,
           size = 1,
           prob = expit(x %*% beta))

```

We then apply the ParSPaS framework and the following figures are created.


```{r, fig.width=9, fig.height=6}
output = ParSPaS::parspas(x = x,
                          y = y,
                          B = 100,
                          I = 20,
                          family = "binomial",
                          seed = 1234)
ParSPaS::combine_plot(output$plots)
```

